%-------------------------
% Resume in Latex
% Author : Christy Yu
% Based off of: https://github.com/SwiftWinds/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Mateo Wang} \\ \vspace{1pt}
  \small(301) 250-6219 $|$ \href{mailto:christyyu@ucsb.edu}{\underline{christyyu@ucsb.edu}} $|$
  \href{https://www.linkedin.com/in/christyyu/}{\underline{linkedin.com/in/christyyu}} $|$
  \href{https://github.com/qwistaycat}{\underline{github.com/qwistaycat}} $|$
  San Jose, CA
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Carnegie Mellon University}{Aug. 2025 -- Aug. 2026}
{M.S. Human Computer Interaction}{Pittsburgh, PA}
\resumeSubheading
{UC Santa Barbara}{3.75 GPA $|$ Aug. 2021 -- Jun. 2025}
{B.S. Computer Science, B.S. Statistics & Data Science}{Santa Barbara, CA}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineer Intern}{Jun. 2024 -- Aug. 2024}
{Lorentz Solution}{Santa Clara, CA}
\resumeItemListStart
\resumeItem{Migrated all 44 dynamic libraries from compiler RHEL6 to RHEL78 for PeakView chip-simulation\textbf{(Bash scripting)}}
\resumeItem{Reduced \textbf{10\%} in backup storage and production release package by automating library clean-up process}
\resumeItem{Executed regression unit tests on circuit simulation cases; analyzed, debugged and troubleshot on the updated libraries for
upcoming release of PeakView software}
\resumeItemListEnd

\resumeSubheading
{Research Fellowship}{Jan. 2023 -- Present}
{Human Wildlife Conflict emLab}{UCSB}
\resumeItemListStart
\resumeItem{Build and tune \textbf{habit suitability machine learning models} with bioclimatic variables and land cover data to explore how
climate change drives human-elephant conflict in Namibia in \textbf{R}}
\resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Salesforce Developer Intern}{Oct. 2023 -- Mar. 2024}
{UCSB IT Department}{Santa Barbara, CA}
\resumeItemListStart
\resumeItem{Maintained and implemented Curriculum Planning System web-application \textbf{(Javascript)}}
\resumeItem{Built petition forms section with \textbf{Salesforce Flows} in Student Success Hub framework}
\resumeItemListEnd

\resumeSubheading
{Design and Marketing Lead Organizer}{Aug. 2023 -- June. 2025}
{SBHacks Hackathon}{UCSB}
\resumeItemListStart
\resumeItem{Orchestrated a 48-hour hackathon, bringing together 200+ students from 20+ universities to address environmental
sustainability, health, and accessibility through coding projects}
\resumeItem{Draw assets, design UI layout, and designed branding system for hackathon page to maintain visual theme across websites
and social media \textbf{(Figma, Photoshop)}}
\resumeItemListEnd

\resumeSubheading
{Coding Team Research Assistant}{Sept. 2022 -- Jun. 2023}
{Louis Lab Sensory Systems Behavior}{UCSB}
\resumeItemListStart
\resumeItem{Implemented Direct Linear Transformation(DLT) method in \textbf{Python OpenCV script} to turn 3D real-world coordinates to
2D pixels on dual raspberry pi arduino camera \textbf{(Computer Vision)}}
\resumeItem{Implemented virtual light-dispersement plume model in \textbf{Python} script to study behavior of Drosophila fly larvae}
\resumeItemListEnd

\resumeSubheading
{Data Visualization Director}{Jun. 2021 -- Jun. 2023}
{The Daily Nexus Newspaper (Data Team)}{UCSB}
\resumeItemListStart
\resumeItem{Produced NLP unsupervised topic classification data visualizations with \textbf{NLTK} on Taylor Swift lyrics in article}
\resumeItem{Coded interactive web-interface to map students' geographical background in analysis article \textbf{(D3 Javascript)}}
\resumeItem{Hosted workshops, wrote guideline documents, answered questions and advised 100+ members during biweekly check-up
meetings on making professional data visualizations for publication}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/heyyysus/refract}{\underline{Refract}}}} $|$ {Anti-deepfake Identity Protection App, Data Science Club Project Team}{Jan. 2024 - May. 2024}
\resumeItemListStart
\resumeItem{Designed and developed frontend mobile app \textbf{(Tailwind/Javascript/CSS, Figma)}, that disrupt deepfake model training against identity theft from images, poster winning 2nd in annual showcase}
\resumeItem{Cloaked images disrupts deepfake models by \textbf{70\%} with no visual difference to the human eye}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Newsletter Curator App}} $|$ {UIUX Project Manager & Designer, SB Creative Lab}{Apr. 2024 - Jun. 2024}
\resumeItemListStart
\resumeItem{Conducted \textbf{UX research} by surveying and interviewing individuals to identify pain points, consolidated results in user personas, analyzed competing brands}
\resumeItem{Manage project timeline and resources, delegated tasks weekly, and composed case study}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://github.com/Ononymous/Noteblockit}{\underline{Noteblockit}}}} $|$ {Multi-Instrument MP3 to Midi Converter, Data Science Club Project Team}{Mar. 2023 - Apr. 2023}
\resumeItemListStart
\resumeItem{Created MP3 to MIDI converter that can preserve multiple instrumental melodies, overcoming the limitation that most Midi converters flatten to a single melody with \textbf{RNN} modeling}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Other projects on \href{https://github.com/qwistaycat?tab=repositories}{\underline{GitHub}}}}
\resumeSubHeadingListEnd


%
%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: Python, C++, Java, HTML/CSS/Javascript, Bash, R, SQL, MATLAB, SAS, Scheme} \\
        \textbf{Frameworks and Libraries}{: Numpy, Matplotlib, Pandas, Seaborn, Plotly, React, Tailwind, Wallace: Maxent, Scikit-Learn,
        Pytesseract, Sobel Edge-Detection, OpenCV, NLTkit, pyLDAvis, React, Tailwind CSS} \\
        }}
\end{itemize}

\end{document}